formula1_start_vs_finish.Rmd

### 2024-04-10 inst/formula1_start_vs_finish.Rmd
another plot for 2022

```{r}
dotchart(mH2,pch=16)
dotchart(log(mH2),pch=16)
```

@@

>>>>

```{r maketwodotcharts}
dotchart(mH2,pch=16)
dotchart(log(mH2),pch=16)
```

```{r showanexampleoff,cache=TRUE}
o <- likelam(lambda=0.9, topn=15,finish=finish,grid=grid)
loglik(equalp(o),o)

o <- likelam(lambda=0.95, topn=15,finish=finish,grid=grid)
loglik(equalp(o),o)

```

@@

```{r plotbigmat22}
like <- bigmat[1,]
like <- like - max(like)
plot(lam,like,type='b')
abline(h=c(0,-2))
```
